### 2016-02-11 reviews/answer_to_revieweres.txt

> Line 48 - '52% or up to 52%' need to verify the fact

ANSWER: From Crossa et al: around 52% and 58% in two maize datasets; from Poland et al: quoting from the text "up to 80% missing data per marker" (Page 105)

> Line 55 -57 - imputation method has been developed for SNP-Chips. I am not sure about the accuracy of statement

ANSWER: sentence modified to "Most methods for genotype imputation have been applied to SNP array data, and typically yield very high imputation accuracy". [see P3, L55-56]

@@

> 1. Why these two species? They have very different properties which makes it difficult to associate the differences in results to particular characteristics. For example, is ploidy level more critical than a reference genome?  It might have been more insightful when including an outbred diploid species with a reference genome and similar to the rice to assess imputation accuracy with and without reference genome information.

ANSWER: we decided to use two very different species to cover a wide range of possible outcomes. The core idea is to follow the well known practice of having an easy benchmark and a difficult one, as it is often done in machine learning community. Moreover, while a general study with several species and datasets would be desirable, it was out of the scope of the current work (and effort). The paper results are consistent both internally and with the cited literature, and we think shine some light on the examined topic, even without the use of many different datasets.
We however understand the reasoning in the reviewer's question, and decided to adjust the declared target of the paper to be less general and focus more on the studied species. The change of title goes in that direction, as much as a big part of the updated text.

> 2. A missed opportunity to study the utilization of a reference genome of a related species, as is available for alfalfa

ANSWER: We followed the reviewer advice and added the results of aligning on Medicago truncatula genome.

@@

> 6. No attention to results on individual rice chromosomes. In case there were no clear differences between chromosomes, then that should be stated more clearly.

ANSWER: we made this aspect more clear (in short: no big differences between chromosomes).

Specific comments
> Line 52: It would be nice if you could provide a list of associated packages, AND explain why Beagle was selected out of these methods.

ANSWER: we added several references to software sources. [e.g. reference to a review on software for (animal) genomics, + reference to all software used in the paper: e.g. Beagle, Tassel, R packages]

@@

> Line 175: Were the eigenvectors of M’M and MM’ merged to arrive at the ‘first k eigenvectors’?

ANSWER: the columns of matrix U contain the eigenvectors of MM' (n x n matrix), the columns of matrix V contain the eigenvectors of M'M (m x m matrix). The n diagonal elements of matrix Sigma (n x m) are the square root of the eigenvalues of matrix U (n x n) (which should correspond also to the non-zero eigenvalues of V' / M'M). The first k eigenvectors of U were then determined based on the ordered corresponding eigenvalues. The matrix U* (n x k) contains these k eigenvectors, which multiplied by the k regression coefficients in vector beta return the (n x 1) column vector of estimated genotypes at locus j. This has been made clearer in the text [P8, L189-199]

> Line 178: Which value for k was used, was there a decision criteria used?

ANSWER: we used K = 4. After some trials (data not shown) we found that no big difference are found in the 3-20 range. Also, K = 4 is the same used by Rutkoski et al.. This was added to the text [P9, L209-211]

@@

> Line 185 – 198: Explain the ‘hat’ for U in equation 2. Also, why has Y no hat while there is a hat on the Y in equation 3.

ANSWER: the hat on U was a mistake and therefore removed; it is not a matrix of estimated values. However, we used the superscript U*, since this is the matrix of the first k eigenvectors of U, and therefore it is not equal to U. In equation [2], Y is the vector of observations (no hat); in equation [3] Y is the vector of predicted values (hat).

> Line 217: Elaborate on the content of this likelihood file or provide a reference (to the manual of Beagle)?

ANSWER: more details were added to the text, plus a reference to the Beagle Manual [P10, L236-240]

@@

> Line 347: Rather extensive reporting on computation time which seems not justified as the used methods were used as these were available to the authors, i.e.., there was not dedicated efforts to speed up the implemented methods.

ANSWER: This section has been re-written, shortened where possible, and a statement, in the discussion, on the limitations of the information on computation time was added.

> Line 379-381: Where was this negative impact shown?  In this study or other studies – please include references.

ANSWER: references to Rutkoski et al  and to Annicchiarico et al were added. We tried to explain better the difference between SNP array (~5% missing) and GBS data (~50% missing) [P18, L432-435]

### 2016-02-11 inputs/acknowledgements.tex
acknowledge

\begin{acknowledgements}
The creation of the rice data set was financially supported by the Marie Curie European
Reintegration Grant ``NEUTRADAPT''.
The creation of the alfalfa data sets was funded by the projects ‘Genomic selection in alfalfa (GENALFA)’ funded by the Italian Ministry of Foreign Affairs and International Cooperation in the framework of the Italy-USA scientific cooperation program, the Italian share of the FP7-ArimNet project ‘Resilient, water- and energy-efficient forage and feed crops for Mediterranean agricultural systems (REFORMA)’ funded by the Italian Ministry of Agricultural and Forestry Policies.
\end{acknowledgements}

>>>>

\begin{acknowledgements}
The rice data used in this research paper were produced within the framework of the Italian national project ``RISINNOVA'' (grant n. 2010-2369), financially supported by the AGER Foundation..
The creation of the alfalfa data sets was funded by the projects ‘Genomic selection in alfalfa (GENALFA)’ funded by the Italian Ministry of Foreign Affairs and International Cooperation in the framework of the Italy-USA scientific cooperation program, the Italian share of the FP7-ArimNet project ‘Resilient, water- and energy-efficient forage and feed crops for Mediterranean agricultural systems (REFORMA)’ funded by the Italian Ministry of Agricultural and Forestry Policies.
\end{acknowledgements}
